---
title: "Group Activity (Module 4)"
author: "Karl Boncodin, Andrew Choa, Covi Perfecto, Luis Sevilla and Joshua Tirana"
date: "8/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
## Methodology
## Results
```{r, echo=FALSE}
library(readxl)
newdata <- read_excel("C:/Users/User/Downloads/ev_workplace_charging_data.xlsx")
```
For this situation, we want to test if () with a 95% confidence interval($\alpha$ = 0.05)

Null Hypothesis:

Alternative Hypothesis:

Test Statistic:

The data set provided are in large numbers so we use the console to test the hypothesis.

Reject $H_0$ if: 
	
P-value < 0.05 or $|f_0|$ > $f_{\alpha,1,n-2}$

Computations:

This is one using the code below:
```{r}
TOTKWH <- newdata$kwhTotal
TOTSES <- newdata$totalSessions
simpleregress <- lm(TOTSES ~ TOTKWH, data = newdata)
summary(simpleregress)
```
We find the coefficients for the regression model from the lm function and our regression model would be: 
$$
  \hat{y} ~=~100.7807~-~1.9940x
$$
Also in the lm function, we find out that 

  $f_0$ = 44.75 and a p value = 2.613$e^{-11}$

And based on the criteria for rejection:
$$
  f_0~=44.75~>~f_{0.05,1,3993}~=~3.84~~~and ~~~~P(f_0)=2.613e^{-11}~<~0.05
$$
so we reject $H_0$

Then we test for true correlation where:

Null Hypothesis: $H_0$: $\rho$ = 0

Alternative Hypothesis: $H_0$: $\rho$ $\ne$ 0

Test statistic: We will again use the console to compute for the t test statistic.

Reject $H_0$ if: 
	$|t_0|$ > $t_{\alpha/2,n-2}$

Computations:

We use the code below to get the test statistic for correlation:
```{r}
corellate <- cor.test(TOTKWH, TOTSES, method = "pearson") 
corellate
```
Based on result, our t value is -6.6892 and based on our criteria:

$$
|t_0| = 6.6892 > t_{0.025,3993} = 1.960
$$


Hence, we reject $H_0$ and that the correlation coefficient is $\rho$ $\ne$ 0.

## Discussion

## Conclusion

